---
title: "gov.1005.preci"
author: "Michael Montella"
date: "10/18/2018"
output: html_document
---

```{r setup, include=FALSE, messages = FALSE, echo = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(readxl)
library(tidyverse)
library(janitor)
library(dplyr)
library(htmltools)
```
#### This is the preci for Michael Montella's Gov 1005 final project. This project will focus on the economic relationship between the United States and China. At the present, I am thinking of conducting an economic diagnosis of each respective country's economy and where each economy is headed given the best and most reliable indicators. I have a particular interest in tracking the economic value generated by various areas in both countries; for example, how much economic value is contributed to the US-China economic partnership by Sussex County, NJ. I intend to significantly refine the scope of this project moving forward, but I can confidently assert that the topic will be the US-China economic relationship, as mentioned above. This relationship will affect all of us, and I am particularly interested in better understanding the dynamics of this relationship as a matter of American politics, international relations, and national security. In the coming weeks, I will be reaching out to professors in the Government, Economics, and East Asian Studies Departments to work on refining what I am working toward. Presently, I can think of three professors who might be particularly helpful: Dr Nara Dillon, Gregory Mankiw, and William Kirby. I have past contact with all three of these faculty members, so this short list is more a reflection of familiarity rather than identified expertise. 

```{r, messages = FALSE, echo = FALSE, warnings = FALSE}
UStrade <- read_excel("country.xlsx")
```



